### 2016-10-04 ms/ms.tex
made pailo's comments

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for system-level
  conservation biology. Using a long-term data set comprising nearly
  20,000 pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Species are highly dynamic in their
  network position, causing assembly to be punctuated by
  significant reorganizations of interactions. Non-assembling mature
  hedgerows and weedy field margins did not undergo as many
  significant network reorganizations, suggesting environmental
  factors alone cannot account for the changes observed in assembling
  communities. Pollinator species were opportunistic in the flowers
  they visited. Indeed, the most persistent and generalized
  species were also the most variable in their network positions --- the
  opposite of which would be expected by preferential attachment. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turnover
  at higher rates in assembling hedgerows as the networks continually
  reorganize. Nestedness of assembling networks also increased through
  time, but there was no increase in robustness to simulated plant
  extinctions. The resilience of networks to cascading perturbations,
  however, increased as the communities assembled, at least partially
  due to accumulating species richness. Our results elucidate some of
  the mechanisms underlying plant-pollinator network assembly and
  restoration, while providing further evidence that hedgerows are a
  valuable tool for promoting species conservation and ecosystem
  provision in agricultural areas.
\end{abstract}

@@

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, forup2008restoration,
  devoto2012understanding}, suggesting interactions are evolving as
the community develops. Understanding the mechanisms of network
assembly will help to guide community restoration. Facilitating
network restoration is especially imperative in areas where species
interactions provide essential ecosystem services, such as crop
pollination. In intensively managed agricultural landscapes, the
demand for pollination services is the greatest
\citep{kremen-2008-10}. However, honey bees, managed extensively
around the world to provide crop pollination, are in global decline
\citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In addition, native
pollinators, which are capable of providing sufficient crop
pollination \citep{kremen-2002-16816, winfree-2007-1105,
  kremen-2004-1109}, are in short supply because these landscapes make
poor habitats for pollinator populations \citep{kremen-2002-16816}. To
ensure the continued provision of ecosystem services and curb
biodiversity loss, it is critical to restore pollinators and their
interactions in agricultural landscapes. To promote pollinator
services in agriculture, farmers may chose to plant strips of native
plants along farm edges (hedgerows) to help provide habitat for
pollinators without removing arable land from production. Hedgerows
augment the richness, abundance and trait diversity of pollinators in
agricultural landscapes \citep{morandin-2013-829, mgonigle-2015-x,
  kremen-2015-602, ponisio2015farm}. In addition, hedgerows promote
the persistence and colonization of floral resource specialists
\citep{mgonigle-2015-x}. Little is known, however, about how new
species are being incorporated into the network as the community
assembles, or the consequences for interaction patterns and
robustness.

%% Lauren I would put 10 year dataset; and I *loved* the way you
%% organized the ideas here!!
We explore the process of network development using a nine year
dataset of plant-pollinator communities assembly following hedgerow
restoration in the highly simplified and intensively managed
agricultural landscape of California's Central Valley.  We first
determine whether the mechanism underlying network assembly is a
smooth build up of interactions as would be predicted by preferential
attachment, or punctuated by significant reorganizations of
interactions (i.e., network changing points). Even with changing
points in interaction organization, networks could still be assembling
via preferential attachment if the network reorganizations were
primarily driven the by peripheral, temporally variable species while
a stable, well-connected core of species persist. We test whether the
species that are most variable in their network position --- and thus
important contributors to network reorganizations --- are less persistent
and connected species. To further explore the mechanisms underlying
the temporal dynamics of the networks, we examine patterns in the
species and interaction temporal turnover. Lastly, we investigate
whether networks are assembling toward predictable interaction
patterns, and the ramifications for the robustness of the networks to
species extinction and cascading perturbations.

@@

We surveyed plant-pollinator interaction networks of assembling
hedgerows communities (N=5), as well as in two types of non-assembling
communities to serve as controls: unrestored, weedy field margins
(N=19) and mature hedgerows (greater than 10 years since planting,
N=29). The sites were located in the Central Valley of California in
Yolo, Colusa and Solano Counties. This area is composed of intensively
managed agriculture --- primarily monocultures of conventional row
crops, vineyards and orchards. Hedgerows we planted along field
margins where they do not remove valuable land from
production. Plantings are between are ca.~3--6 m wide and
approximately 350 m long, bordering large (ca.\ 30--hectare) crop
fields. Hedgerows consist of native, perennial, shrub and tree
plantings including \textit{Rosa californica}, \textit{Cercis
  occidentalis}, \textit{Ceanothus spp.}, \textit{Heteromeles
  arbutifolia}, \textit{Sambucus mexicana}, \textit{Eriogonum spp.},
\textit{Baccharis spp.}, \textit{Salvia spp}. and others
\citep{kremen-2015-602, mgonigle-2015-x}. The mean distance between
monitoring sites was 15 km, and the minimum distance between sites of
the same type sampled in the same year was 2 km.  The entire area
surveyed spanned almost 300 km$^2$. The crop fields adjacent to all
sites were similarly managed as intensive, high-input monoculture.

@@

\subsection*{Change point analysis}
\subsubsection*{Identifying change points}
We employed a change point detection method \citep{peel2014detecting}
to identify fundamental reorganizations in large-scale interaction
patterns. A change point is caused by a merge, split, fragmentation or
formation of communities (also called modules or compartments). Change
point detection methods have yet to be generalized to quantitative
networks, so for this analysis we focused on qualitative (binary)
networks. Following \cite{peel2014detecting}, we first defined a
probability distribution over the networks using the generalized
hierarchical random graph model (GHRG). The GHRG model is able to
capture both assortative and disassortative community structure
patterns at all scales in the network \citep{peel2014detecting}. A
network $G$ is composed of vertices $V$ and edges $E$. The GHRG model
decomposes the $N$ vertices into a series of nested groups, the
relationships among which are represented by the dendrogram $T$. The
tips of $T$ are the vertices of $G$, and the probability that two
vertices $u$ and $v$ connect is given by the parameter $p_r$. The
probability distribution of the network $G$ thus defined as:

@@

We next test whether the change points occurring in maturing hedgerows
were a component of the assembly process or a product of environmental
shifts that lead to network reorganizations in all types of
communities. We model the number of change points as successes and the
total number of years each site was sampled as trails, and use a
generalized linear model with Binomial error to test whether the
probability of a change point occurring varied by site type. We used
standard techniques to determine whether the assumptions of the models
were met for this and all subsequent models. For the non-assembling
hedgerows and weedy field margins, only sites with five or greater
survey years were included in this analysis. All statistical analysis
were conducted in R 3.2.3 \citep{R}.

@@

We calculate species persistence as the proportion of surveys in which
a plant or pollinator is observed. Species observed consistently
within and between years are thus maximally persistent. Weighted
species degree is calculated from interaction observations from an
extensive dataset from Yolo County (approx.~18000 interaction records)
that included both the data included in this study and additional data
from sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness at each site through time. Closeness describes the
centrality of a species in the network by calculating path lengths to
other vertices (species) in the graph. We use linear mixed models to
test whether the species closeness variability (log) is related to the
persistence or degree of that species \citep{lme4, lmetest}. We
included random effects for species, as well as site. Because the
degree and persistence of pollinators were strongly correlated, ($\rho
= 0.84$, $p$-value $<$ $2*10^{-16}$), we include each explanatory
variable in the model separately. Plant degree and persistence were
not significantly correlated, but we use the same models as we did for
the pollinators for consistency. A linear increase in closeness, as
might be expected with assembly by preferential attachment, would also
lead to a high variability in closeness scores, so we test whether
closeness increases through time.

@@

%%Lauren I really liked the way you explained this part =]
Reorganizations of network structure can be the result of species
turnover or species changing their interaction partners (i.e.,
re-wiring). To better understand the mechanisms underlying the
temporal dynamics of the assembling networks, we examined patterns of
species and interaction turnover. For example, assembling networks may
have higher rates of pollinator turnover than non-assembling
communities because new pollinator species are colonizing and
establishing themselves \citep{mgonigle-2015-x}. Similarly, if
pollinators try to maximize their foraging efficiency based on the
species present, interactions may turnover more quickly than in
established communities. In addition, at assembling hedgerows, plants
may ``colonize'' the networks as they become more attractive
resources, and establish new interactions with pollinators.

@@

\subsection*{Network robustness}
Lastly, we test whether the changes in interaction patterns associated
with network assembly affect the robustness of the network to species
loss and to cascading perturbations. Following \cite{Memmott2004}, we
simulate plant species extinction and the subsequent extinction
cascades of pollinator species. Because the reproduction of plant
species if facilitated by active restoration efforts, it is unlikely
the extinction of pollinator species would affect plant populations in
the hedgerows. However, plants ceasing to bloom, for example in
response to drought, will likely affect the pollinators that depend on
them. We eliminate plants species based on their degree or abundance,
and then calculate the number of pollinators that secondarily went
extinct. The area below the extinction curve is an estimate of network
robustness \citep{Memmott2004, bipartite}.

We also explored how the robustness to cascading perturbations changed
as community assembled, using algebraic connectivity --- the second
smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., submitted). Algebraic connectivity relates to how
difficult it is to turn a network into completely disconnected groups
of species \citep{costa2007characterization}. The larger the algebraic
connectivity, the more robust a network is to cascading perturbations,
and the harder it is to break the community into isolated groups of
species (Gaiarsa et al., submitted).

@@

In contradiction to the predictions of assembly by preferential
attachment, both pollinator persistence and degree were positively
related to network position variability (Fig.~\ref{fig:cv}, estimate
of the slope of closeness variability and persistence $\pm$ standard
error of the estimate, $0.653 \pm 0.225$, $p$-value=$0.009$; slope of
closeness variability and degree, $0.008 \pm 0.002$,
$p$-value=$0.002$). In addition, plant persistence and degree were not
significantly related to network position variability
(Fig.~\ref{fig:cv}, estimate of the slope of closeness variability and
persistence $\pm$ SE, $-2.063 \pm 3.091$,
$p$-value=$0.5$; slope of closeness variability and degree, $0.0018
\pm 0.002$, $p$-value=$0.3$). The variability of species network
position was not the result of closeness linearly increasing through
time, and, in fact, plant and pollinator closeness decreased slightly
through time (Fig.~S2, estimate of the slope of closeness through time
$\pm$ SE, pollinators: $-0.0003 \pm
0.00005$, $p$-value=$2.7*10^{-12}$; plants $-0.007 \pm 0.001$,
$p$-value=$1.4*10^{-6}$). Through statistically significant, the
slopes are so slight they may not be biologically significant.

@@

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
Network nestedness significantly increased with assembly
(Fig.~\ref{fig:baci}, estimate of the slope of nestedness through time
$\pm$ SE, $1.834 \pm 0.6142$,
$p$-value=$0.022$). Modularity decreased (Fig.~\ref{fig:baci}),
though the slope was not significantly different from zero (estimate
of the slope of modularity through time $\pm$ standard error of the
estimate, $-0.524$ $\pm$ $0.295$, $p$-value=$0.124$). Connectance
decreased as the community assembled (Fig.~\ref{fig:baci}, estimate of
the slope of connectance through time $\pm$ standard error of the
estimate, $-0.0434$ $\pm$ $0.0152$, $p$-value=$0.03$). In contrast,
specialization remained constant (estimate of the slope of
specialization through time $\pm$ SE,
$0.003$ $\pm$ $0.015$, $p$-value=$0.827$).

@@

\subsection*{Network robustness}
Assembly did not effect the robustness of the networks to species
extinction when species where removed incrementally by degree
(Fig.~\ref{fig:rob}, estimate of the slope of robustness through time
$\pm$ SE, $6*10^{-5} \pm 4*10^{-3}$, $p$-value=$0.987$) or abundance
($0.001 \pm 0.003$, $p$-value=$0.65$). In contrast, the robustness of
networks to cascading perturbations, as measured by the algebraic
connectivity of the network, increased as the network assembled
(Fig.~\ref{fig:rob}, estimate of the slope of robustness to cascading
perturbations through time $\pm$ SE, $0.6814 \pm 0.272$,
$p$-value=$0.042$).

@@

In addition to finding multiple network organization changing points
during assembly, the way in which these reorganizations occur was
different from what is expected by preferential attachment Based on a
preferential attachment process, we expect that the most persistent
and high degree species would remain stable in the network core during
assembly. Surprisingly, however, we encountered the opposite
pattern. For example, the four most ubiquitous species in our study
landscape --- \textit{Halictus ligatus}, \textit{Halictus
  tripartitus}, \textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- were the only species that changed
which module (i.e., community) they were a member across years in all
the assembling hedgerows. Because species degree and persistence were
strongly correlated, it is difficult to disentangle the causal
mechanism for why species with those characteristics are so variable
in their network position. Generalized species may be able to better
exploit the limited floral resources in the intensively managed
agriculture landscape, and thus also be the most persistent. More
persistent species usually have longer phenologies, so they can visit
many different flowers, resulting in a higher degree. Either way, our
result suggests that adaptable species can change their network
position to utilize the most advantageous floral resources available,
which may depend on the other pollinator species that are present, and
the state of the plant community. Thus given the opportunity and
ability to use different resources, species will often change their
network positions.

@@

When we explore the how the network-level interaction patterns changed
through time, we found that nestedness did increase as the community
assembled, as would be expected if colonizing, specialist species
preferentially attached to a central, generalist core
\citep{albrecht2010plant}. In addition, connectance decreased, as
would be expected if the network is being colonized by specialist
species and the overall mean number of interactions per species did
not change. With preferential attachment, however, we would also
expect specialization to increase, and we found no such
trend. Furthermore, the frequent changing points in network
organization, dynamic nature of species positions in the networks, and
turnover of species and interactions all point to an assembly
mechanism other than preferential attachment.  The stable level of
network-level specialization through the assembly process may be due
to the increased colonization of specialized species
\citep{mgonigle-2015-x} accompanied by an increase in the diet breath
of resident species. This would be expected if resident species were
able to minimize their foraging time by expanding their diet breath as
plant diversity increases with hedgerow maturation \citep{Waser1996,
  pyke1984optimal, Bluthgen2007, albrecht2010plant}. Such a change in
pollinator behavior would also explain the increase in network
nestedness. Because so many mechanisms give rise to the same patterns
of interaction, additional tests are necessary to assess the contribution
of different mechanisms to community assembly.

@@

Plant-pollinator networks, in general, are highly dynamic, with high
turnover of species and interactions both within and between seasons
\citep{Burkle2011}. Though our non-assembling communities experience
fewer network reorganizations than the assembling hedgerows, $82\%$ of
field margins and $40\%$ of mature hedgerows underwent at least one
changing point in network structure. Pollinators are also highly
opportunistic \citep{petanidou-2008-564, Vazquez2005b,
  albrecht2010plant}, though trait complementarity such as tongue
length and corolla depth impose some biophysical limits to the
interactions between plants and pollinators
\citep{Vazquez2009evaluating, Vazquez2009, Stang2009, Stang2006,
  Santamaria2007}. Such opportunism may buffer plant-pollinator
communities from global change \citep[e.g.,][]{ramos2012topological,
  kaiser2010robustness}, but our limited understanding of the assembly
of these communities impedes making such predictions
\citep{Vazquez2009, Burkle2011}. Unlike in the broader food web
literature, we have few mechanistic models of mutualistic network
assembly \citep{valdovinos2013adaptive, Nuismer2013, Guimaraes2011}.
In addition, the few developed often borrow their mechanisms from
competitive interactions, leading to inaccurate biological assumptions
\citep{holland2006comment}. We need further development of mechanistic
models of mutualistic systems to generate testable predictions, along
with empirical exploration of network assembly. Plant-pollinator
communities and mutualisms broadly are vital for biodiversity
maintenance and essential ecosystem service provision. We must
therefore understand the processes underlying their assembly to
facilitate restoration and conservation.

@@

We would like to thank Paulo Guimar{\~a}es, Aaron Clauset and Matthew
Hutchinson for their invaluable discussions and comments, and Leto
Peel for help with the change point analysis.  We thank the growers
and land owners that allowed us to work on their property. We also
greatly appreciate the identification assistance of expert taxonomists
Martin Hauser, Robbin Thorp and Jason Gibbs.  This work was supported
by funding from the Army Research Office (W911NF-11-1-0361 to CK), the
Natural Resources Conservation Service (CIG-69-3A75-12-253,
CIG-69-3A75-9-142, CIG-68-9104-6-101 and WLF-69-7482-6-277 to The
Xerces Society), the National Science Foundation (DEB-0919128 to CK),
The U.S.  Department of Agriculture (USDA-NIFA 2012-51181-20105 to
Michigan State University).  Funding for LCP was provided by an NSF
Graduate Research Fellowship, the USDA NIFA Graduate Fellowship, and
the Berkeley Institute for Data Science. Funding for MPG was provided
by S{\~a}o Paulo Research Foundation (FAPESP, grant 2013/13319-5). We
also appreciate the Santa Fe Institute for faciliting this
international collaboration.

>>>>

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for system-level
  conservation biology. Using a long-term data set comprising nearly
  20,000 pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing assembly to be punctuated
  by significant reorganizations of interactions. In contrast, the
  non-assembling networks did not restructure as frequently. Across
  all communities, Pollinator species were opportunistic in the
  flowers they visited. Indeed, the most persistent and generalized
  species were also the most variable in their network positions. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turnover
  at higher rates in assembling hedgerows as the networks continually
  reorganize. Nestedness of assembling networks also increased through
  time, but there was no increase in robustness to simulated plant
  extinctions. Our results elucidate some of the mechanisms underlying
  plant-pollinator network assembly and restoration, while providing
  further evidence that hedgerows are a valuable tool for promoting
  species conservation and ecosystem provision in agricultural areas.
\end{abstract}

@@

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, forup2008restoration,
  devoto2012understanding}, suggesting interactions are changing as
the community develops. Understanding the mechanisms of network
assembly will help to guide community restoration. Facilitating
network restoration is especially imperative in areas where species
interactions provide essential ecosystem services, such as crop
pollination. In intensively managed agricultural landscapes, the
demand for pollination services is the greatest
\citep{kremen-2008-10}. However, honey bees, managed extensively
around the world to provide crop pollination, are in global decline
\citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In addition, native
pollinators, which are capable of providing sufficient crop
pollination \citep{kremen-2002-16816, winfree-2007-1105,
  kremen-2004-1109}, are in short supply because these landscapes make
poor habitats for pollinator populations \citep{kremen-2002-16816}. To
ensure the continued provision of ecosystem services and curb
biodiversity loss, it is critical to restore pollinators and their
interactions in agricultural landscapes. To promote pollinator
services in agriculture, farmers may chose to plant strips of native
plants along farm edges (hedgerows) to help provide habitat for
pollinators without removing arable land from production. Hedgerows
augment the richness, abundance and trait diversity of pollinators in
agricultural landscapes \citep{morandin-2013-829, mgonigle-2015-x,
  kremen-2015-602, ponisio2015farm}. In addition, hedgerows promote
the persistence and colonization of floral resource specialists
\citep{mgonigle-2015-x}. Little is known, however, about how new
species are being incorporated into the network as the community
assembles, or the consequences for interaction patterns and
robustness.

%% Lauren I would put 10 year dataset; and I *loved* the way you
%% organized the ideas here!!
We explore the process of network development using a nine year
dataset of plant-pollinator communities assembly following hedgerow
restoration in the highly simplified and intensively managed
agricultural landscape of California's Central Valley.  We first
determine whether the mechanism underlying network assembly is a build
up of interactions as would be predicted by preferential attachment,
or punctuated by significant reorganizations of interactions (i.e.,
network changing points). Even with changing points in interaction
organization, networks could still be assembling via preferential
attachment if the network reorganizations were primarily driven the by
peripheral, temporally variable species while a stable, well-connected
core of species persist. We test whether the species that are most
variable in their network position --- and thus important contributors
to network reorganizations --- are less persistent and connected
species. To further explore the mechanisms underlying the temporal
dynamics of the networks, we examine patterns in the species and
interaction temporal turnover. Lastly, we investigate whether networks
are assembling toward predictable interaction patterns, and the
ramifications for the robustness of the networks to species
extinction.

@@

We surveyed plant-pollinator interaction networks of independent
assembling hedgerows communities (N=5), as well as in two types of
non-assembling communities to serve as controls: unrestored, weedy
field margins (N=19) and mature hedgerows (greater than 10 years since
planting, N=29). The sites were located in the Central Valley of
California in Yolo, Colusa and Solano Counties. This area is composed
of intensively managed agriculture --- primarily monocultures of
conventional row crops, vineyards and orchards. Hedgerows we planted
along field margins where they do not remove valuable land from
production. Plantings are between are ca.~3--6 m wide and
approximately 350 m long, bordering large (ca.\ 30--hectare) crop
fields. Hedgerows consist of native, perennial, shrub and tree
plantings including \textit{Rosa californica}, \textit{Cercis
  occidentalis}, \textit{Ceanothus spp.}, \textit{Heteromeles
  arbutifolia}, \textit{Sambucus mexicana}, \textit{Eriogonum spp.},
\textit{Baccharis spp.}, \textit{Salvia spp}. and others
\citep{kremen-2015-602, mgonigle-2015-x}. The mean distance between
monitoring sites was 15 km, and the minimum distance between sites of
the same type sampled in the same year was 2 km.  The entire area
surveyed spanned almost 300 km$^2$. The crop fields adjacent to all
sites were similarly managed as intensive, high-input monoculture.

@@

\subsection*{Change point analysis}
\subsubsection*{Identifying change points}
We employed a change point detection method \citep{peel2014detecting}
to identify fundamental reorganizations in large-scale interaction
patterns. A change point is caused by a merge, split, fragmentation or
formation of modules (also called compartments). Change point
detection methods have yet to be generalized to quantitative networks,
so for this analysis we focused on qualitative (binary)
networks. Following \cite{peel2014detecting}, we first defined a
probability distribution over the networks using the generalized
hierarchical random graph model (GHRG). The GHRG model is able to
capture both assortative and disassortative structure patterns at all
scales in the network \citep{peel2014detecting}. A network $G$ is
composed of vertices $V$ and edges $E$. The GHRG model decomposes the
$N$ vertices into a series of nested groups, the relationships among
which are represented by the dendrogram $T$. The tips of $T$ are the
vertices of $G$, and the probability that two vertices $u$ and $v$
connect is given by the parameter $p_r$. The probability distribution
of the network $G$ thus defined as:

@@

We next test whether the change points occurring in maturing hedgerows
were a component of the assembly process or a product of environmental
shifts that lead to network reorganizations in all types of
communities. We model the number of change points as successes and the
total number of years each site was sampled as trails, and use a
generalized linear model with Binomial error to test whether the
probability of a change point occurring varied by site type. We used
standard techniques to determine whether the assumptions of the models
were met for this and all subsequent models. For the non-assembling
hedgerows and weedy field margins, only sites with five or greater
survey years were included in this analysis (N=11). All statistical
analysis were conducted in R 3.2.3 \citep{R}.

@@

We calculate species persistence as the proportion of surveys in which
a plant or pollinator is observed. Species observed consistently
within and between years are thus maximally persistent. Weighted
species degree is calculated from interaction observations from an
extensive dataset from Yolo County (approx.~18000 interaction records)
that included both the data included in this study and additional data
from sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness centrality \citep{freeman1978centrality} at each
site through time. Closeness centrality describes the centrality of a
species in the network by calculating path lengths to other vertices
(species) in the graph \citep{freeman1978centrality}. We use linear
mixed models to test whether the species closeness variability (log)
is related to the persistence or degree of that species \citep{lme4,
  lmetest}. We included random effects for species, as well as
site. Because the degree and persistence of pollinators were strongly
correlated, ($\rho = 0.84$, $p$-value $<$ $2*10^{-16}$), we include
each explanatory variable in the model separately. Plant degree and
persistence were not significantly correlated, but we use the same
models as we did for the pollinators for consistency. An approximately
logarithmic increase in closeness centrality, as would be expected
with assembly by preferential attachment, would also lead to a high
variability in closeness scores, so we test whether log closeness
centrality increases through time.

@@

%%Lauren I really liked the way you explained this part =]
Reorganizations of network structure can be the result of species
turnover or species changing their interaction partners (i.e.,
re-wiring). To better understand the mechanisms underlying the
temporal dynamics of the assembling networks, we examined patterns of
species and interaction turnover. For example, assembling networks may
have higher rates of pollinator turnover than non-assembling
communities because new pollinator species are colonizing and
establishing themselves \citep{mgonigle-2015-x}. Similarly, if
pollinators try to maximize their foraging efficiency based on the
species present, interactions may turnover more quickly than in
established communities. In addition, at assembling hedgerows,
unvisited plants may appear to ``colonize'' the networks as they
establish new interactions with pollinators.

@@

\subsection*{Network robustness}
Lastly, we test whether the changes in interaction patterns associated
with network assembly affect the robustness of the network to species
loss. Following \cite{Memmott2004}, we simulate plant species
extinction and the subsequent extinction cascades of pollinator
species. Because the reproduction of plant species if facilitated by
active restoration efforts, it is unlikely the extinction of
pollinator species would affect plant populations in the
hedgerows. However, plants ceasing to bloom, for example in response
to drought, will likely affect the pollinators that depend on them. We
eliminate plants species based on their degree or abundance, and then
calculate the number of pollinators that secondarily went extinct. The
area below the extinction curve is an estimate of network robustness
\citep{Memmott2004, bipartite}.

% We also explored how the robustness to cascading perturbations changed
% as community assembled, using algebraic connectivity --- the second
% smallest eigenvalue of the Laplacian matrix
% \citep{fiedler1973algebraic} --- as a proxy for network robustness
% (Gaiarsa et al., submitted). Algebraic connectivity relates to how
% difficult it is to turn a network into completely disconnected groups
% of species \citep{costa2007characterization}. The larger the algebraic
% connectivity, the more robust a network is to cascading perturbations,
% and the harder it is to break the community into isolated groups of
% species (Gaiarsa et al., submitted).

@@

In contradiction to the predictions of assembly by preferential
attachment, both pollinator persistence and degree were positively
related to network position variability (Fig.~\ref{fig:cv}, estimate
of the slope of closeness centrality variability and persistence $\pm$
standard error of the estimate, $0.653 \pm 0.225$, $p$-value=$0.009$;
slope of closeness centrality variability and degree, $0.008 \pm
0.002$, $p$-value=$0.002$). In addition, plant persistence and degree
were not significantly related to network position variability
(Fig.~\ref{fig:cv}, estimate of the slope of closeness variability and
persistence $\pm$ SE, $-2.063 \pm 3.091$, $p$-value=$0.5$; slope of
closeness variability and degree, $0.0018 \pm 0.002$,
$p$-value=$0.3$). The variability of species network position was not
the result of closeness linearly increasing through time, and, in
fact, plant and pollinator closeness decreased slightly through time
(Fig.~S2, estimate of the slope of closeness through time $\pm$ SE,
pollinators: $-0.0003 \pm 0.00005$, $p$-value=$2.7*10^{-12}$; plants
$-0.007 \pm 0.001$, $p$-value=$1.4*10^{-6}$). Through statistically
significant, the slopes are so slight they may not be biologically
significant.

@@

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
Network nestedness significantly increased with assembly
(Fig.~\ref{fig:baci}, estimate of the slope of nestedness through time
$\pm$ SE, $1.834 \pm 0.6142$, $p$-value=$0.022$). Modularity decreased
(Fig.~\ref{fig:baci}), though the slope was not significantly
different from zero (estimate of the slope of modularity through time
$\pm$ standard error of the estimate, $-0.524$ $\pm$ $0.295$,
$p$-value=$0.124$). In addition, none of the networks were
significantly modular ($z$-scores $<$ 2, Fig.~\ref{fig:baci})
Connectance decreased as the community assembled (Fig.~\ref{fig:baci},
estimate of the slope of connectance through time $\pm$ standard error
of the estimate, $-0.0434$ $\pm$ $0.0152$, $p$-value=$0.03$). In
contrast, specialization remained constant (estimate of the slope of
specialization through time $\pm$ SE, $0.003$ $\pm$ $0.015$,
$p$-value=$0.827$).

@@

\subsection*{Network robustness}
Assembly did not effect the robustness of the networks to species
extinction when species where removed incrementally by degree
(estimate of the slope of robustness through time $\pm$ SE, $6*10^{-5}
\pm 4*10^{-3}$, $p$-value=$0.987$) or abundance ($0.001 \pm 0.003$,
$p$-value=$0.65$). % In contrast, the robustness of
% networks to cascading perturbations, as measured by the algebraic
% connectivity of the network, increased as the network assembled
% (Fig.~\ref{fig:rob}, estimate of the slope of robustness to cascading
% perturbations through time $\pm$ SE, $0.6814 \pm 0.272$,
% $p$-value=$0.042$).

@@

In addition to finding multiple network organization changing points
during assembly, the way in which these reorganizations occur was
different from what is expected by preferential attachment. Based on a
preferential attachment process, we expect that the most persistent
and high degree species would remain stable in the network core during
assembly \citep{barabasi1999emergence}. Surprisingly, however, we
encountered the opposite pattern. For example, the four most
ubiquitous species in our study landscape --- \textit{Halictus
  ligatus}, \textit{Halictus tripartitus}, \textit{Lasioglossum
  (Dialictus) incompletum}, and \textit{Toxomerus marginatus} --- were
the only species that changed which module they were a member across
years in all the assembling hedgerows. Because species degree and
persistence were strongly correlated, it is difficult to disentangle
the causal mechanism for why species with those characteristics are so
variable in their network position. Generalized species may be able to
better exploit the limited floral resources in the intensively managed
agriculture landscape, and thus also be the most persistent
\flagged{any citations? I can only find articles discussing
  generalization in plants}. More persistent species usually have
longer phenologies, so they can visit many different flowers,
resulting in a higher degree \citep{Vazquez2009}. Either way, our
result suggests that adaptable species can change their network
position to utilize the most advantageous floral resources available,
which may depend on the other pollinator species that are present, and
the state of the plant community \citep{macleod2016measuring,
  gomez2006ecological, waser1996generalization}. Thus given the
opportunity and ability to use different resources, species will often
change their network positions \citep{macleod2016measuring}.

@@

When we explore the how the network-level interaction patterns changed
through time, we found that nestedness did increase as the community
assembled, as would be expected if colonizing, specialist species
preferentially attached to a central, generalist core
\citep{albrecht2010plant}. In addition, connectance decreased, as
would be expected if the network is being colonized by specialist
species and the overall mean number of interactions per species did
not change. However, the frequent changing points in network
organization, dynamic nature of species positions in the networks, and
turnover of species and interactions all point to an assembly
mechanism other than preferential attachment.  The stable level of
network-level specialization through the assembly process may be due
to the increased colonization of specialized species
\citep{mgonigle-2015-x} accompanied by an increase in the diet breath
of resident species. This would be expected if resident species were
able to minimize their foraging time by expanding their diet breath as
plant diversity increases with hedgerow maturation \citep{Waser1996,
  pyke1984optimal, Bluthgen2007, albrecht2010plant}. Such a change in
pollinator behavior would also explain the increase in network
nestedness. Because so many mechanisms give rise to the same patterns
of interaction, additional tests are necessary to assess the
contribution of different mechanisms to community assembly.

@@

Plant-pollinator networks, in general, are highly dynamic, with high
turnover of species and interactions both within and between seasons
\citep{Burkle2011}. Though our non-assembling communities experience
fewer network reorganizations than the assembling hedgerows, $82\%$ of
field margins and $40\%$ of mature hedgerows underwent at least one
changing point in network structure. Pollinators are also highly
opportunistic \citep{petanidou-2008-564, Vazquez2005b,
  albrecht2010plant}, though trait complementarity such as tongue
length and corolla depth impose some biophysical limits to the
interactions between plants and pollinators
\citep{Vazquez2009evaluating, Vazquez2009, Stang2009, Stang2006,
  Santamaria2007}. Such opportunism may buffer plant-pollinator
communities from global change \citep[e.g.,][]{ramos2012topological,
  kaiser2010robustness}, but our limited understanding of the assembly
of these communities impedes making such predictions
\citep{Vazquez2009, Burkle2011}. Unlike in the broader food web
literature, we have few assembly models of mutualistic network
assembly \citep{valdovinos2013adaptive, Nuismer2013, Guimaraes2011}.
In addition, the few developed models often borrow their mechanisms
from competitive interactions, leading to inaccurate biological
assumptions \citep{holland2006comment}. We need further development of
mechanistic models of mutualistic systems to generate testable
predictions, along with empirical exploration of network
assembly. Plant-pollinator communities and mutualisms broadly are
vital for biodiversity maintenance and essential ecosystem service
provision. We must therefore understand the processes underlying their
assembly to facilitate restoration and conservation.

@@

We would like to thank Paulo R.~Guimar{\~a}es Jr., Aaron Clauset and Matthew
Hutchinson for their invaluable discussions and comments, and Leto
Peel for help with the change point analysis.  We thank the growers
and land owners that allowed us to work on their property. We also
greatly appreciate the identification assistance of expert taxonomists
Martin Hauser, Robbin Thorp and Jason Gibbs.  This work was supported
by funding from the Army Research Office (W911NF-11-1-0361 to CK), the
Natural Resources Conservation Service (CIG-69-3A75-12-253,
CIG-69-3A75-9-142, CIG-68-9104-6-101 and WLF-69-7482-6-277 to The
Xerces Society), the National Science Foundation (DEB-0919128 to CK),
The U.S.  Department of Agriculture (USDA-NIFA 2012-51181-20105 to
Michigan State University).  Funding for LCP was provided by an NSF
Graduate Research Fellowship, the USDA NIFA Graduate Fellowship, and
the Berkeley Institute for Data Science. Funding for MPG was provided
by S{\~a}o Paulo Research Foundation (FAPESP, grant 2013/13319-5). We
also appreciate the Santa Fe Institute for faciliting this
international collaboration.
